Combinatorial interpretations of holonomic recurrences

### 2021-09-08 article/main.tex
Fix typo in lstlisting

c.append_r_class_subtree_visitor(-1,                # negative node
    lambda kind, left, right:
        None if kind[0] is None else                # we ignore all virtual nodes
        ["l", kind] + left + right + [(None, "*")]  # for each actual node we add
                                                    # l node with right virtual
                                                    # node pointed as a~parent
)
\end{lstlisting}
\todo{Repeat in natural language}

>>>>

c.append_r_class_subtree_visitor(-1,                # negative node
    lambda kind, left, right:
        None if kind[0] is None else                # we ignore all virtual nodes
        ["l", kind] + left + right + [(None, "*")]  # for each actual node we add
                                                    # l node with right virtual
                                                    # node pointed as a parent
)
\end{lstlisting}
\todo{Repeat in natural language}
